\textbf{ Discovery of a disrupting open cluster far into the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2019-05-09 ms.tex
add uncertainties and update values

\newcommand{\clage}{\ensuremath{130~\textrm{Myr}}}
\newcommand{\clfeh}{\ensuremath{-1.1}}
\newcommand{\cldist}{\ensuremath{29~\textrm{kpc}}}

@@

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau \approx \clage$, distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
We find that the inferred extinction, $A_V \approx 0.33$, is somewhat larger than the value $A_{V, {\rm SFD}} \approx 0.2$ from the SFD dust map \citep{Schlegel:1998}.
We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.

@@

\begin{table}[htb]
\begin{center}
    \begin{tabular}{ r | l | l}
        \multicolumn{3}{c}{\textbf{Inferred properties of \clustername}} \\
        \toprule
        Name & Value & Description \\
        \tableline
        $\mean{\alpha}$ & $178.8^\circ$ & right ascension \\
        $\mean{\delta}$ & $-29.4^\circ$ & declination \\
        $\mean{D}$ & $28.9 \pm 0.1~\kpc$ & Heliocentric distance \\
        $\mean{\mu_\alpha}$ & $-0.56 \pm 0.04~\masyr$ & proper motion in RA\\
        $\mean{\mu_\delta}$ & $0.47 \pm 0.02~\masyr$ & proper motion in Dec\\
        \tableline
        $\tau$ & $130 \pm 6~\textrm{Myr}$ & age \\
        $M$ & $1200~\msun$ & total stellar mass \\
        $\feh$ & $-1.10 \pm 0.02$ & metallicity \\
        \tableline
        $A_V$ & $0.33 \pm 0.02$ & extinction \\
        \toprule
    \end{tabular}
\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername.
Formal precisions on all inferred parameters are very small, typically one to a few per cent, but we suspect that systematic errors with the photometry and isochrone models limit the accuracy of these measurements to $\sim 5\%$.
\label{tbl:clusterparams}}
\end{center}
\end{table}

>>>>

\newcommand{\clage}{\ensuremath{116~\textrm{Myr}}}
\newcommand{\clfeh}{\ensuremath{-1.14}}
\newcommand{\cldist}{\ensuremath{28.7~\textrm{kpc}}}

\newcommand{\clageerr}{\ensuremath{116 \pm 7~\textrm{Myr}}}
\newcommand{\clfeherr}{\ensuremath{-1.14 \pm 0.05}}
\newcommand{\cldisterr}{\ensuremath{28.7 \pm 0.4~\textrm{kpc}}}
\newcommand{\claverr}{\ensuremath{0.21 \pm 0.02}}

@@

We use the posterior samples from the hierarchical inference described in \sectionname~\ref{sec:popmodel} to compute the posterior probabilities that each source in the \decam\ CMD selection box (red box, \figurename~\ref{fig:decam-cmd}) is a member of the cluster.
\figurename~\ref{fig:hierarch-iso} shows the \decam\ photometry for all sources with membership probability $> 0.5$ (circle markers).
Over-plotted in \figurename~\ref{fig:hierarch-iso} (blue, solid line) is a \acronym{MIST} isochrone with the median posterior parameters derived from the hierarchical modeling, shifted to the median distance and extincted given the median $A_V$ value.
\changes{We find that \clustername\ is indeed young, distant, and metal poor, with median posterior values of age $\tau = \clageerr$, distance $D = \cldisterr$, and metallicity $\feh = \clfeherr$ (see also \tablename~\ref{tbl:clusterparams} for a summary).
We find that the inferred extinction, $A_V = \claverr$, is consistent with the value $A_{V, {\rm SFD}} \approx 0.2$ from the (revised) SFD dust map \citep{Schlegel:1998, Schlafly:2011}.}
We note again that, with the \decam\ photometry, we are limited to studying the subcomponent a of \clustername\ --- follow-up imaging of component b (see \figurename~\ref{fig:cmds}) would enable a similar analysis for the full cluster.

@@

\begin{table}[htb]
\begin{center}
    \begin{tabular}{ r | l | l}
        \multicolumn{3}{c}{\textbf{Inferred properties of \clustername}} \\
        \toprule
        Name & Value & Description \\
        \tableline
        $\mean{\alpha}$ & $178.8^\circ$ & right ascension \\
        $\mean{\delta}$ & $-29.4^\circ$ & declination \\
        $\mean{D}$ & $28.7 \pm 0.4~\kpc$ & Heliocentric distance \\
        $\mean{\mu_\alpha}$ & $-0.56 \pm 0.04~\masyr$ & proper motion in RA\\
        $\mean{\mu_\delta}$ & $0.47 \pm 0.02~\masyr$ & proper motion in Dec\\
        \tableline
        $\tau$ & $116 \pm 7~\textrm{Myr}$ & age \\
        $M$ & $1200~\msun$ & total stellar mass \\
        $\feh$ & $-1.14 \pm 0.05$ & metallicity \\
        \tableline
        $A_V$ & $0.21 \pm 0.02$ & extinction \\
        \toprule
    \end{tabular}
\caption{This table summarizes the measured or inferred kinematic and stellar population parameters of the young halo stellar cluster \clustername.
Formal precisions on all inferred parameters are very small, typically one to a few per cent, but we suspect that systematic errors with the photometry and isochrone models limit the accuracy of these measurements to $\sim 5\%$.
\label{tbl:clusterparams}}
\end{center}
\end{table}
